Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-03-29 paper/AlignedIsotropicGW.tex
Added section on effect of small spin magnitudes -- can be cut if not agreed upon, included to make decision easier

>>>>

\section{Effect of small spin magnitudes}
\label{sec:smallspins}

In the main text we considered three models for BH spin magnitudes: ``low'', ``flat'' and ``high''. These were intended to capture some of the uncertainty regarding the BH spin magnitude distribution.

Here we extend the ``low'' model as:
%
\begin{equation}
p(a) \propto (1 - a)^{\alpha}
\label{eq:lowspinalpha}
\end{equation}
%

When $\alpha = 0$, this recovers the ``flat'' distribution, whilst $\alpha = 1$
recovers the ``low'' distribution. For higher values of $\alpha$, this distribution 
becomes more peaked towards $a = 0$.

%
\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{../plots/sigma_v_alpha.png}
\caption{\textbf{Effect of small spins on evidence ratio of aligned against isotropic models} The blue line shows the evidence ratio (plotted as the equivalent sigma) between a model where all systems are aligned, versus one where all systems are from an isotropic distribution as a function of the power law $\alpha$ corresponding to Equation~\ref{eq:lowspinalpha}.  The top axis shows the mean spin magnitude $a$
that the value of alpha corresponds to. We see that for mean spin magnitudes $\lesssim 0.2$ we find no evidence for either distribution over the other.}
\label{fig:smallspinsalpha}
\end{figure}
%

In Figure~\ref{fig:smallspinsalpha} we plot the evidence ratio of aligned to isotropic distributions (plotted as the equivalent sigma) with spin magnitudes given by this model with $\alpha$ in the range $0$ -- $6$. The top axis I shows the mean spin magnitude
that value of alpha corresponds to (i.e., for the ``flat'' distribution $\alpha = 0$, the mean spin magnitude is 0.5). We see that if typical BH spins are $\lesssim 0.2$ we have no evidence for one model over the other.
